\documentclass[10pt]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\pagenumbering{gobble}
\usepackage{titlesec}
\titleformat{\section}[block]{\fontsize{13}{13}\selectfont\bfseries}{}{0em}{}[\titlerule]
\setlength{\parindent}{0pt}
\newcommand{\cventry}[1]{\hangindent=1.5em\hangafter=1 #1\par\medskip}
\newcommand{\cvsep}{\par\medskip}


\begin{document}
\begin{center}
    {\LARGE \textbf{Gracie Zeller}} \\
    gzeller2@wisc.edu | 920-850-1512
\end{center}
\vspace{0.1in}
\section*{Education}
\textbf{University of Massachusetts Amherst} \hfill Amherst, MA \\
PhD student, Psychology (Cognition and Cognitive Neuroscience) \hfill to start 09/2026 \\
Advisor: Benjamin Pitt, PhD
\cvsep
\textbf{University of Wisconsin–Madison} \hfill Madison, WI \\
BS, Anthropology, and Psychology \hfill 05/2025 \\
GPA: 3.96/4.0
\section*{Research Experience}
\textbf{Laboratory Manager} \hfill 05/2025-present \\
Cognitive Origins Lab \\
PI: Stephen Ferrigno, PhD
\cvsep
\textbf{Undergraduate Research Assistant} \hfill 06/2023-05/2025 \\
Cognitive Origins Lab \\
PI: Stephen Ferrigno, PhD \\
Senior Thesis: \textit{"Rhesus Monkeys Can Apply Hume's Principle in a Quantity Discrimination Task"}
\cvsep
\textbf{Undergraduate Research Assistant} \hfill 09/2024-05/2025 \\
DeLuca Biochemistry Lab \\
PIs: Hector DeLuca, PhD \& Lori Plum, PhD
\section*{Presentations}
\cventry{\textbf{Zeller, G.}, \& Ferrigno, S. (2026, April 10). \textit{One-to-one correspondence in children and monkeys} [Poster]. Cognitive Development Society, Montreal, Québec.}
\cventry{Silva, A., Tramm, E., Kadolph, E., \textbf{Zeller, G.}, Brungardt, S., \& Ferrigno, S. (2026, April 10). \textit{Development of the approximate number system: Accounting for the early life environment in rhesus monkeys} [Poster]. Cognitive Development Society, Montreal, Québec.}
\cventry{Serrano, M., \textbf{Zeller, G.}, \& Ferrigno, S. (2025, August 8). \textit{Perceptual fluency and confidence judgments in early childhood} [Poster]. Letters and Science Summer of Excellence in Research Summer Colloquium, Madison, Wisconsin.}
\cventry{\textbf{Zeller, G.}, \& Ferrigno, S. (2025, April 25). \textit{Rhesus monkeys can use the logic of one-to-one correspondence in a quantity discrimination task} [Poster]. Undergraduate Research Symposium, Madison, Wisconsin.}
\cventry{\textbf{Zeller, G.}, \& Ferrigno, S. (2025, April 10). \textit{One-to-one correspondence logic in rhesus macaques} [Poster]. Midwest Psychological Association, Chicago, Illinois.}
\section*{Awards, Fellowships, \& Honors}
Graduation with Distinction \hfill 2025 \\
Undergraduate Travel Award \hfill 2024 \\
Hilldale Undergraduate/Faculty Research Fellowship \hfill 2024 \\
Margarete E. Lubach Undergraduate Research Award \hfill 2024 \\
Phi Beta Kappa Honor Society \hfill 2024
\section*{Mentoring}
\textbf{UW–Madison} \\
Meredith: sophomore research fellowship \hfill Summer 2025-Spring 2026 \\
Hannah: undergraduate thesis \hfill Fall 2025–Spring 2026
\section*{Outreach}
Panelist, UW-Madison Psychology Dept Graduate School Panel \hfill 04/22/2026 \\
Guest Speaker, Winneconne High School AP Psychology \hfill 10/03/2025 \\
Madison East High School Science Expo Presenter \hfill 10/22/2025 \\
Wisconsin Science Festival Presenter \hfill 2023-2025


\end{document}